---
title: "match_address_to_metro"
author: "Sifan Liu"
date: "4/14/2022"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message=FALSE)
```

## Introduction
Regional analysis often require matching addresses to a standard geography. This tutorial shows how to retrieve the geography coordinates (latitude and longitude) of the addresses, and use spatial joins to find out if the addresses fall inside the target geographies. 

## Required packages

```{r library}
library(dplyr)
library(tidygeocoder)
library(tigris)
library(sf)
library(tmap)
```


## Example: A list of address
Suppose we have a list of addresses, and we want to match the addresses to US metropolitan areas.

```{r address}
(add <- tidygeocoder::sample_addresses)
```

## Geocoding
First, we use `tidygeocoder` package to perform batch geocoding. 
See documentations here: https://jessecambon.github.io/tidygeocoder/articles/geocoder_services.html

```{r geocode}

geocoded <- add %>% 
  tidygeocoder::geocode(address = addr, method = "arcgis")

geocoded

```

## Shapefiles
Next, we retrieve shapefiles of the target geographies from US Census. `tigris` package proivides shapefiles for counties, metro areas, states, and many other census geographies. 

```{r shapefiles}
cbsa_shapes <- tigris::core_based_statistical_areas(cb = T)

# how the shapes look like on a map
tm_shape(cbsa_shapes)+
  tm_borders()
```


## Spatial Joins
To perfrom spatial joins, we first need to convert the lat long columns from character value to a spatial object with `sf::st_as_sf` function. Make sure to use the same Coordinate Reference Systems (CRS) as the shapefiles. 

Finally, we use `sf::st_intersection` function to figure out if any address **points** falls into the metro **shapes**. The output shows the final matching result.

```{r joins}
geocoded %>% 
  select(name, addr, lat, long) %>% 
  st_as_sf(coords = c("long", "lat"), crs = st_crs(cbsa_shapes)) %>% 
  st_intersection(cbsa_shapes) %>% 
  st_drop_geometry() %>% 
  select(name, addr, cbsa_code = GEOID)


```


